ODGI: understanding pangenome graphs

### 2022-02-10 manuscript/fig_extract_viz_draw_position_untangle.tex
Bandage is not in ODGI

        \textbf{(f)} \textit{Bandage}~\citep{Wick_2015} layout of the C4 pangenome graph, annotated by using \textit{odgi position}. Green nodes indicate the C4 genes. The red rectangle highlights the regions where \textit{C4A} and \textit{C4B} genes differ.
        \textbf{(g)} Annotated \textit{bandage} layout of the C4 region where \textit{C4A} and \textit{C4B} genes differ due to single nucleotide variants leading to changes in the encoded protein sequences. Node labels were annoted by using \textit{odgi position}.

>>>>

        \textbf{(f)} \REVIEWED{Layout of the C4 pangenome graph made with the \textit{Bandage} tool~\citep{Wick_2015} and} annotated by using \textit{odgi position}. Green nodes indicate the C4 genes. The red rectangle highlights the regions where \textit{C4A} and \textit{C4B} genes differ.
        \textbf{(g)} Annotated \textit{Bandage} layout of the C4 region where \textit{C4A} and \textit{C4B} genes differ due to single nucleotide variants leading to changes in the encoded protein sequences. Node labels were annoted by using \textit{odgi position}.
